---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# areaPD

<!-- badges: start -->
<!-- badges: end -->

The goal of areaPD is to calculate phylogenetic diversity (PD)
for a set of geographic areas, calculating endemism PD for the
set of areas, calculating complementarity PD given a selected 
area, and constructing a Venn's diagram of PD within and between 
areas, given one or more phylogenetic trees and an assignment of 
samples (e.g., alleles, species, etc.) to areas.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arleyc/areaPD")
```
## Example

```{r example1}
library(areaPD)
#PD calculation for a set of areas and a given phylogeny
data("homodata")
data("homotree")
homoPD<-multiareaPD(homodata[1:5,],homotree)
limnoPD<-multiareaPD(limnodata[1:5,],limnotree)
contoPD<-multiareaPD(contodata[1:5,],contotree)
latiPD<-multiareaPD(latidata[1:5,],latitree)
```

```{r example2}
#complementary PD calculation for a set of areas given a phylogeny
#(in red) and a selected area (LCL, in green)
homoPDcomp<-compareaPD(homodata[1:5,],homotree,LCL)
```

```{r example3}
#endemism PD calculation for a set of areas given a phylogeny
homoPDend<-endemismPD(homodata[1:5,],homotree)
```

```{r example4}
#drawing a Venn's diagram for a set of five areas given four
#different phylogenetic trees
vennout<-makeVennPD(list(homoPD,limnoPD,contoPD,latiPD))
```
