---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# areaPD

<!-- badges: start -->
<!-- badges: end -->

The functions in areaPD can calculate phylogenetic diversity (PD)
and endemism PD for a set of geographic areas, the complementarity
PD given a selected area, and constructing a Venn's diagram of PD within and between areas, given one or more phylogenetic trees and an assignment of samples (e.g., alleles, species, etc.) to areas.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arleyc/areaPD")
```
## Example

```{r example1}
library(areaPD)
#PD calculation for a set of areas and a given phylogeny
data("homodata")
data("homotree")
homoPD<-multiareaPD(homodata[1:5,],homotree)
limnoPD<-multiareaPD(limnodata[1:5,],limnotree)
contoPD<-multiareaPD(contodata[1:5,],contotree)
latiPD<-multiareaPD(latidata[1:5,],latitree)
```

```{r example2}
#complementarity PD calculation for a set of areas given a phylogeny
#(in red) and a selected area (LCL, in green)
homoPDcomp<-compareaPD(homodata[1:5,],homotree,LCL)
```

```{r example3}
#endemism PD calculation for a set of areas given a phylogeny
homoPDend<-endemismPD(homodata[1:5,],homotree)
```

```{r example4}
#drawing a Venn's diagram for a set of five areas given four
#different phylogenetic trees
vennout<-makeVennPD(list(homoPD,limnoPD,contoPD,latiPD))
```

## References

Faith, P. D. (1992) Conservation evaluation and phylogenetic
diversity. Biological Conservation, 61, 1-10.

Faith, P. D. (2016) The PD phylogenetic diversity framework:
linking evolutionary history to feature diversity for biodiversity
conservation. In: Biodiversity Conservation and Phylogenetic
Systematics, Topics in Biodiversity and Conservation, 14,
DOI 10.1007/978-3-319-22461-9_3.

Faith, P. D., Reid, C. A. M., and Hunter, J. (2004) Integrating
phylogenetic diversity, complementarity, and endemism for
conservation assessment. Conservation Biology, 18, 255-261.

Moritz, C., and Faith, D. P. (1998) Comparative phylogeography
and the identification of genetically divergent areas for
conservation. Molecular Ecology, 7, 419-429.

## Citation

Camargo, A., Elgue, E., Fernandez, F., Lima, L., and Maneyro, R. (2023) Conservation prioritization of the northern hills of Uruguay based on the intra-specific phylogenetic diversity of frogs and lizards. Journal for Nature Conservation, 75, 126468. doi: 10.1016/j.jnc.2023.126468 
