---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# areaPD

<!-- badges: start -->
<!-- badges: end -->

The goal of areaPD is to calculate phylogenetic diversity (PD)
for a set of geographic areas, calculating complementarity PD 
given a selected area, and constructing a Venn's diagram of PD 
within and between areas, given a phylogenetic tree and an 
assignment of samples (e.g., alleles, species, etc.) to areas.

## Installation

You can install the released version of areaPD from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("areaPD")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("arleyc/areaPD")
```
## Example

```{r example1}
library(areaPD)
#PD calculation for a set of areas and a given phylogeny
data("homodata")
data("homotree")
homoPD<-multiareaPD(homodata,homotree)
data("limnodata")
data("limnotree")
limnoPD<-multiareaPD(limnodata,limnotree)
data("contodata")
data("contotree")
contoPD<-multiareaPD(contodata,contotree)
data("latidata")
data("latitree")
latiPD<-multiareaPD(latidata,latitree)
```

```{r example2}
#complementary PD calculation for a set of areas given a phylogeny 
# (in red) and a selected area (LCL, in green)
homoPDcomp<-compareaPD(homodata,homotree,LCL)
limnoPDcomp<-compareaPD(limnodata,limnotree,LCL)
contoPDcomp<-compareaPD(contodata,contotree,LCL)
latiPDcomp<-compareaPD(latidata,latitree,LCL)
```

```{r example3}
#drawing a Venn's diagram for a set of five areas given two
#different phylogenetic trees
vennout<-makeVennPD(list(homoPD,limnoPD,contoPD,latiPD))
```
